---
title: "Homework 9 : Functions and Programming"
author: "Brianna Green"
date: "11/24/2020"
output: github_document
---
# 1. Write a function that takes two vectors of the same length and returns the number of positions that have an NA in both vectors.
``` {r}
x <- c(3, 6, 9, 12)
variance.num <-function(x, na.rm=TRUE){
  n <-length(x)
  m <-mean(x, na.rm=TRUE)
  sq_err <-(x-m)^2
  sum(sq_err)/(n-1)
}

print(variance.num(x))
#Numeric vector=x, n=length function, m=mean and use equation from exercise
```
# 2. Write both\_na(), a function that takes two vectors of the same length and returns the number of positions that have an NA in both vectors
```{r, message=FALSE}
skew.num <-function(x, na.rm=FALSE){
  v <-variance.num(x, na.rm=na.rm)
  n <-length(x)
  m <-mean(x, na.rm=na.rm)
  (sum((x-m)^3/(n-2))/v^(3/2))
}

print(skew.num(x))
```
# 3. Write a function to create a specific kind of plot, with useful labels, etc., that can take a data frame as an argument.
```{r, message=FALSE}
data_plot <-function(x,y){
  x <-c(2,3,6,7)
  y <-c(1,2,3,4)
  p <-ggplot(data, aes_string(x,y))+
    geom_point()
    xlab("x data")
    ylab("y data")
}
```
# 4. Write a function that takes one argument and does the following
## If argument is a numeric vector, multiples every number in the vector by 2. If argument is a character vector, sorts the vector into alphabetical order. If argument is anything else, issues an information warning and returns the argument unchanged.

```{r, message=FALSE}
jack_of_trades <-function(arg) {
  go <-if(is.numeric(arg)) {
    arg*2
  } else if(is.character(arg)) {
  sort(arg)
  } else if(!is.numeric(arg)) if(!is.character(arg)) {
  warning("Entry needs to be either a numeric vector or character vector")
  }
  go
}
```
# 5. Write a function that tries to calculate the mean of a vector using mean ().
## This line calculates the mean of the vector 'x'.
```{r, message=FALSE}
mean(is.na(x))
```
## This line calculates vector 'x' divided by the sum of the vector 'x'.
```{r, message=FALSE}
x / sum(x, na.rm = TRUE)
```
# 6. Use system.time() to compare how long it takes to add two, 1-million-element random vectors and store the result in a third vector.
## You have to download library(microbenchmark) in order to perform these lines of code.
```{r, message=FALSE}
system.time(for (i in 1:1000000) {i+i})
```
## Calculates the elapsed time for the system to calculate the function for time that has been pre-allocated.
```{r, message=FALSE}
pre_allo <-numeric(0)
  system.time(pre_allo <-c(for(i in 1:1000000) {i+i}))
```
## Calculates the elapsed time for the system to calculate the function for time that has NOT been pre-allocated.
```{r, message=FALSE}
  system.time(not_pre_allo <-for(i in 1:1000000) {i+i})
```
## In these 2 lines of code I created 2 vectors with a million random elements and used the "sample" function that says to r 'randomly pick 1000000 numbers from the integers 1:1000000'.
```{r, message=FALSE}
million_1 <-sample(x=1000000, 1000000)
million_2 <-sample(x=1000000, 1000000)
```