---
title: "hw_10"
author: "Brianna Green"
date: "11/10/2020"
output: github_document
---

# Linear Model
Using the diamonds dataset, create a linear model of price as a function of the weight of the diamond (carat). According to that model, what price would you expect for a 1-carat diamond?

```{r, message=FALSE}
library(tidyverse)
```

```{r}
mod <-lm(price ~carat + color,data=diamonds)
summary(mod)
mod_unordered <-lm(price ~carat+factor(color,ordered=FALSE),
                  data=diamonds)
summary(mod_unordered)
glimpse(diamonds)
summary(mod)
diamonds_mod <-lm(price ~carat, data=diamonds)
mod_char <-lm(price ~carat + factor(color, ordered = FALSE),
              data=diamonds)
```

Now create a linear model of price as a function of carat and color.
What difference does it make if you convert color to a character vector before you make the model? Note that this is probably what you want to do in general, unless you really know what you’re doing.

```{r}
linmod <-lm(price ~carat + color,data=diamonds)
char_linmod <-lm(price ~carat + as.character(color),data=diamonds)
```

Make some plots of the raw data, and of the model fits, to make an argument as to which model is more useful.
Bonus: Should the data have been pre-processed before making these models?
```{r}
linmod <-lm(price ~carat + color,data=diamonds)
char_linmod <-lm(price ~carat + as.character(color),data=diamonds)

#ggplot(diamonds,aes(carat, price))+
#  geom_point()

#basemod <-lm(price ~carat,data=diamonds)
#plot(basemod)
```


# Objects and Methods
```{r}
mtcars_copy <- mtcars
attr(mtcars_copy, "author") <-"Bri"
attr(mtcars_copy, "crazy_data_frame") <-diamonds
attr(mtcars_copy, "vector") <=letters

attr(mtcars_copy, "author")

attr(mtcars_copy, "class") <-"my_new_class"

#write construction function for the "silly_df" class
new_silly_df <-function(x, why_sily= "Because I a giant goofball"){
  if(!is.data.frame(x)) {
    stop("why_silly must be a character vector of length 1")
  }
  if(!(is.character(why_silly) & length(why_silly == 1))){
    stop("why_silly must be a character vector of length 1")
  }
  
  class(x) <-c("silly_df", "data_frame")
  attr(x,"why_silly") <-why_silly
  x
}

#write a summary method for silly_df
summary.silly_df <-function(x) {
  why_silly <- attr(x,"why_silly")
  print(paste0("The resason I'm silly is", why_silly))
  print(summary.data.frame(x))
  summart.data.frame(x)
}

#Write a validator method
validate_silly_df <-function(x) {
  if(is.null(atttr(x, "why_silly"))) {
    stop("why_silly attribute is missing")
  }
  
  # check that it is a valid data frame, too.
}
```



```{r}
mod <-lm(price ~carat + color,data=diamonds)
summary(mod)
mod_unordered <-lm(price ~carat+factor(color,ordered=FALSE),
                   data=diamonds)
summary(mod_unordered)
```