---
title: "Homework 7 : Badplot"
author: "Brianna Green"
date: "10/7/2020"
output: github_document
---
##Badplot
In this bad plot I used a box plot when a point plot would've been more descriptive. I also increased the size of the line connecting the dots in the plot which makes it difficult to see the individual points on the plot and what value they represent. 
```{r}
df <- mtcars[, c("mpg", "cyl", "wt")]
df$cyl <- as.factor(df$cyl)
head(df)
library(ggplot2)
ggplot(df, aes(x=wt, y=mpg)) +
  geom_boxplot(shape=19, fill="blue", color="yellow", size=10)
```

##Better plot
Here I changed the plot to be a scatter plot so it's easier to see which mgp points correspond to weight of the cars. I also adjusted the size so that the values each point is associated with clear. 
```{r}
df <- mtcars[, c("mpg", "cyl", "wt")]
df$cyl <- as.factor(df$cyl)
head(df)
library(ggplot2)
# change shape, color, fill, size
ggplot(df, aes(x=wt, y=mpg)) +
  geom_point(shape=23, fill="purple", color="blue", size=2)
```


