---
title: "Homework 5 : Using R Markdown"
author: "Brianna Green"
date: "09/15/2020"
output: github_document
---
1. Seeing the documentation of flights
```{r}
?nycflights13::flights
```

2. Using the glimpse() function we can get a general sense of the "flights" data frame. There are 336,776 rows and 19 columns.
```{r}
#glimpse(flights)
```

3. Using the filter() function we create a data frame of just the flights that departed 2 hours late or more and we see that 120,382 out of 336,776 flights were delayed by 2 hours.
```{r}
#late_flights <-filter(flights, dep_delay >= 2)
```

4.Using mutate() and paste0 we create a column that contains the combined airline and flight number. 

 This line combines flight and airline number.
```{r}
#flights_combined_airline_and_number <-mutate(late_flights, combined.air.flight.number = paste0(carrier, flight)) 
```
Charts in view to check correct mutation.
```{r}
#glimpse(flights_combined_airline_and_number, !(is.na(tailnum)))
```
Removes flights without a plane tail number.
```{r}
#cleaned_flights <- filter(flights_combined_airline_and_number, tailnum, carrier) 
```

5.Use group() to groups certain flights together. 
```{r}
#cleaned_grouped_flights <-group_by(cleaned_flights, tailnum, carrier)
#glimpse(cleaned_grouped_flights)
#number_of_flights <- summarise(cleaned_grouped_flights, number.of.flights = n())
```
